---
title: "Initial Korean covid 19"
author: "Gema Garcia"
date: "6/21/23"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?


## Methods


We will analyze the Sex of the patients and the result if they are alive or dead. I will use the variables in the collection of cat~cat. Using the helper file, it will help us get the answer to our problem.



## Graphical results - use ggplot commands to do this  



```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
  

Looking at the count graph we see not many are dead. There are about 1400 males alive and around 1700 alive of women. Then looking at the percentage graph, we see the males are dying more than women.Men have a low percentage in being alive and a high percentage in being dead. 

  

## Numerical results


```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```


Looking at the results we see all the people alive are about 56% females and 44% males. The those who are dead are 64% males and 36% females.In the second chart we see 98.7% females are alive and 97% males are alive. Those dead are only 1.4% females and the males are 3%. 



## Inferential results 


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


We see 1831 females are alive and 1411 males are alive . Our p value is 1/1000 and it is a small value. Showing us there is a big difference going on. The second test p value is 9/10000. The odds ratio tells us the odds of a female living are 2x greater than a male living. 




## Conclusions


We used the cat~cat helper file to grab codes and copy them to our file. We would change what needed to be changed to fit our kRdata. We first saw the count and percentage of females and males alive or dead in a gg plot. We saw that males had a higher death percentage than females. In our numerical results we also were able to see how the number of males alive was less than the females alive. The odds ratio helped prove even more that females living are two times greater than males living.  


