---
title: "Initial Korean covid 19"
author: "Gema Garcia"
date: "6/21/23"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?


## Methods


We will analyze the Sex of the patients and the result if they are alive or dead. I will use the variables in the collection of cat~cat. Using the helper file, it will help us get the answer to our problem.



## Graphical results - use ggplot commands to do this  



```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```
  

Looking at the count graph we see not many are dead. There are about 1400 males alive and around 1700 alive of women. Then looking at the percentage graph, we see the males are dying more than women.Men have a low percentage in being alive and a high percentage in being dead. 

  





  
## Numerical results


## Inferential results 




## Conclusions

